Peer influences in air travel behavior: A social autoregressive analysis

### 2015-03-20 article.Rmd
Activated the voice in the survey discussion.

Data Collection
----------------------------------------
To examine the potential for influences to travel behavior between individuals’
within an interconnected social network, a web-based survey was developed, and
respondents were recruited through the Georgia Tech fraternity and sorority
system (a social network that may presumably have a proportionally higher level
of interconnectedness), in partnership with the Georgia Tech Dean of Students,
Office of Greek Affairs.  The web-based survey instrument was distributed via
email to the primary points of contact for each fraternity and sorority on file
at the Office of Greek Affairs.  Fraternities and sororities were asked to also
encouraged to solicit responses from their alumni, thus, potentially increasing
the sample population of approximatley 3,300 students in Greek housing.
Fraternities and sororities were incentivized with the promise of a $500
charitable contribution made on behalf of the fraternity and the sorority each
with the highest participation.

@@

```{r load_user}
user <- readRDS("data/clean/user.rds")
trips <- readRDS("data/clean/trips.rds")
friends <- readRDS("data/clean/friends.rds")
```

Because the survey program collects Facebook profile and friends list data from
the perspective of the respondent's individual profile, it is limited in its
data collection to "visible" user profile and friend data. That is, individuals'
information that was restricted as a result of more stringent individual privacy
settings would not be visible to the survey program. A consequence of this is
potential for imbalance in privacy settings (and thus, data visibility) between
two connections, is that friend connections may be observed as one-way in the
data even though one-way friend connections are not possible on Facebook.

>>>>

Data Collection
----------------------------------------
To examine the potential for influences to travel behavior between individuals’
within an interconnected social network, we developed a web-based survey 
and recruited respondents through the Georgia Tech fraternity and sorority
system (a social network that may presumably have a proportionally higher level
of interconnectedness than the general student population), in partnership with 
the Georgia Tech Dean of Students, Office of Greek Affairs. We distributed the
web-based survey instrument via email to the primary points of contact for each
fraternity and sorority on file at the Office of Greek Affairs. To increase the 
sampling frame potentially beyond the 3,300 currrent fraternity and sorority 
members, we encouraged the organizations to solicit responses from their alumni
groups. The fraternity and sorority with the highest response volumes each
had a $500 donation made in their name to a national charitable organization.

@@

```{r load_user}
trips <- readRDS("data/clean/trips.rds")
user <- readRDS("data/clean/user.rds")
friends <- readRDS("data/clean/friends.rds")
```

Because the survey program collects Facebook profile and friends list data from
the perspective of the respondent's individual profile, it is limited in its
data collection to "visible" user profile and friend data. That is, individuals'
information that was restricted as a result of more stringent individual privacy
settings would not be visible to the survey program. A consequence of this is
that one-way friendships, may be observed in the data even though one-way 
friend connections are not possible on Facebook.
